A Data-Driven Framework for Neural Field Modelling

### 2010-11-16 ltx/first_order_framework/LaTeX_Manuscript.tex
up to experiment iV of results for Davids edits

Figure~\ref{fig:Figure11} demonstrates the affect of the sigmoid parameters on the estimation accuracy. The RMSE of the reconstructed connectivity kernel was calculated for various parameters of the sigmoid by varying the slope, $\varsigma$, and the threshold, $v_0$. The other model parameters remained fixed and where set according the Table~\ref{tab:Parameters}.

% The size of the squares in the figure show the magnitude of the log of the error. The squares are black if the log of the error is negative (the RMSE is $<1$) and the squares are white if the log of the error is positive (the RMSE is $>1$). The largest black squares indicate the best performance and the largest white squares indicate the worst performance for the parameter combinations (\dean{need some thing more quantitative}). 
From the figure it can be seen that the estimation accuracy is inter-related to the properties of the sigmoid function. When the threshold is negative or the slope is very gentle, all of the activity is being passed through the sigmoid function. However, as the slope is increased or the threshold is increased, more information is being cut off or attenuated by the activation function. This is illustrated in Figure~\ref{fig:sigmoidfunctions}, where the sigmoids from the bottom left corner through to near top right corner of Figure~\ref{fig:Figure11} are plotted. This appears to have a detrimental effect on the estimation accuracy.

\subsubsection{Results for Varying the Sensor Kernel Width}
The accuracy of the estimation algorithm was tested for observation kernels by varying the width parameter. Figure~\ref{fig:Figure12} shows the RMSE of the connectivity kernel estimates for the various connectivity kernel widths. The figure shows that there is error a desirable connectivity kernel width range. As the the theory presented earlier in Section~\ref{SpectralAnalysisSection} suggests, the observation kernel acts as a spatial filter. When the observation kernel is to narrow, a small amount of aliasing appears to be increasing the estimation error. When the observation kernel width is initially increased the error drops. As expected when the observation kernel becomes too large, important spatial frequency information is lost and the error becomes larger.

@@

\begin{figure*}[!ht]
\begin{center}
\includegraphics{./Graph/pdf/RMSESigmoidParameters.pdf}
\end{center}
\caption{{\bf RMSE of different kernel estimates}. Log of the RMSE of the kernel for different values of firing threshold, $v_0$ and the slope of the sigmoid, $\varsigma$. Mean kernel estimates are obtained over 50 realisations in each case. White spaces indicate cases where the kernel can not be estimated due to numerical problems.}
\label{fig:Figure12}
\end{figure*}

>>>>

Figure~\ref{fig:Figure12} demonstrates the effect of the sigmoid parameters on the estimation accuracy. The RMSE of the reconstructed connectivity kernel was calculated for various parameters of the sigmoid by varying the slope, $\varsigma$, and the threshold, $v_0$. The other model parameters remained fixed and were set according the Table~\ref{tab:Parameters}.

% The size of the squares in the figure show the magnitude of the log of the error. The squares are black if the log of the error is negative (the RMSE is $<1$) and the squares are white if the log of the error is positive (the RMSE is $>1$). The largest black squares indicate the best performance and the largest white squares indicate the worst performance for the parameter combinations (\dean{need some thing more quantitative}). 
From Figure~\ref{fig:Figure12} it can be seen that the estimation accuracy depends the parameters of the sigmoid function. \dean{This next bit is CRAP (help):} When the threshold is negative or the slope is very gentle, all of the activity is being passed through the sigmoid function. However, as the slope is increased or the threshold is increased, more of the field is within the saturating region of the activation function. This is illustrated in Figure~\ref{fig:sigmoidfunctions}, where the sigmoids from the bottom left corner through to near top right corner of Figure~\ref{fig:sigmoidfunctions} are plotted. This appears to have a detrimental effect on the estimation accuracy.

\subsubsection{Experiment IV: Results for Varying the Sensor Kernel Width}
The accuracy of the estimation algorithm was tested for observation kernels by varying the width parameter. Figure~\ref{fig:Figure12} shows the RMSE of the connectivity kernel estimates for the various connectivity kernel widths. The figure shows that there is error a desirable connectivity kernel width range. As the the theory presented earlier in Section~\ref{SpectralAnalysisSection} suggests, the observation kernel acts as a spatial filter. When the observation kernel is to narrow, a small amount of aliasing appears to be increasing the estimation error. When the observation kernel width is initially increased the error drops. As expected when the observation kernel becomes too large, important spatial frequency information is lost and the error becomes larger.

@@

\begin{figure*}[!ht]
\begin{center}
\includegraphics{./Graph/pdf/RMSESigmoidParameters.pdf}
\end{center}
\caption{{\bf RMSE of different kernel estimates}. Log of the RMSE of the kernel for different values of firing threshold, $v_0$, and the slope of the sigmoid, $\varsigma$. Mean kernel estimates are obtained over 50 realisations in each case. White spaces indicate cases where the kernel can not be estimated due to numerical problems.}
\label{fig:Figure12}
\end{figure*}
